### 2015-02-26 paper/main.tex
added shiny graphic for showing boxplot of dsc-shrink results
updated paper

Since its introduction in 1995 by Benjamini and Hochberg 
\cite{benjamini1995controlling}, the ``False Discovery Rate" (FDR) has quickly established itself
as a key concept in modern statistics, and the primary tool by which most practitioners handle large-scale multiple testing.

@@

 \subsection*{Notation, and existing methods}

Suppose that we are interested in the values of $J$ ``effects" $\beta_j$ ($j=1,\dots,J$). In some contexts our interest may focus on which of the $\beta_j$ are ``significantly" different from zero, whereas in other contexts our interest may focus on estimating their values; the methods described here are suited to both these contexts.
 We assume that we have obtained data $D_1,\dots,D_J$ that provide independent estimates $\bhat_1,\dots,\bhat_J$ of these effects,
 with corresponding (estimated) standard errors $\shat_1,\dots,\shat_J$. For our purposes, these estimates and standard errors could be obtained from the data
 using any method, provided they (approximately) satisfy 
 \begin{equation} \label{eqn:betahat-t}
 \bhat_j \big{|} \, \beta_j, \shat_j \sim t_\nu(\beta_j,\shat_j),
 \end{equation}
for some known degrees of freedom (\df) $\nu$, where $t_\nu(\mu,\sigma)$ denotes the generalized $t$ distribution on $\nu$ \df, with mean $\mu$ and scale parameter $\sigma$. (Equivalently, $(\bhat_j-\beta_j)/\shat_j \big{|} \, \beta_j \sim t_\nu$, where $t_\nu$ denotes the standard $t$ distribution on $\nu$ \df.)
In the special case $\nu \rightarrow \infty$ this includes the situation where the $\bhat$ can be considered normally distributed:
  \begin{equation} \label{eqn:betahat-norm}
 \bhat_j  \big{|} \, \beta_j, \shat_j \sim N(\beta_j,\shat^2_j).
 \end{equation}
 Assuming (\ref{eqn:betahat-t}), the $t$-statistics defined by
 \begin{equation} 
 t_j:=\bhat_j/\shat_j
 \end{equation}
 have a $t_\nu$ distribution under the $j$th null hypothesis $H_j:\beta_j=0$, and this fact can be used to compute a $p$ value $p_j$ testing $H_j$.
Some methods for FDR analysis require $z$ scores instead of $t$ statistics or $p$ values; these methods can be applied by translating each $t_j$ into a corresponding
$z$ score, $z_j$.

One nice feature of the False Discovery Rate (FDR) is that Frequentist and Bayesian definitions are closely aligned.
Here we provide Bayesian definitions, and refer the reader to \cite{storey.03}, particularly his Theorem 1,  for connections with frequentist definitions.
The (tail) FDR at threshold $T$ is defined as
\begin{equation}
\FDR(T) := \Pr(\text{$H_j$ false} | t_j \geq T).
\end{equation}
The local FDR at $t$ is defined \cite{efron2008microarrays} as
\begin{equation}
\fdr(t) := \Pr(\text{$H_j$ is false} | t_j = t).
\end{equation}
The local FDR is perhaps more relevant than the tail FDR, but less widely used, perhaps because
it is harder to estimate (density estimation is harder than tail area estimation). 
The $q$ value for observation $j$ is defined \cite{storey.03} as:
\begin{equation}
q_j := \FDR(t_j).
\end{equation}
That is, the $q$ value for observation $j$ is the FDR if we reject the null for all observations that are at least as significant as observation $j$.

Mention correspondance between fdr and FDR?
Tidy to deal with fact that definitions I give here implicitly assume $\fdr(t)$ etc don't depend on $j$.
Mention that Frequentist and Bayesian alignment depends on assumptions?

One standard genomics analysis pipeline is to take the $p$ values $p_1,\dots,p_J$ and convert them to (estimated) $q$ values $q_1,\dots,q_J$
 using the R package \qvalue. Figure \ref{fig:qvalue} shows a graphical illustration of the procedure implemented in \qvalue. 
 In brief, the idea is that the overall distribution of $p$ values can be decomposed into two constitutive
 components: one component corresponding to the ``null" tests, and a second component corresponding to the ``alternative" tests. 
To perform this decomposition, \qvalue makes two key assumptions:
  i) the null $p$ values have a uniform distribution, and ii) the $p$ values near 1 are all from
 tests where the null is true. Under these assumptions performing the decomposition boils down to 
 drawing the horizontal line on the $p$ value histogram that intersects with the distribution at $p=1$: the area under this horizontal
 line defines the uniform component that is due to the null $p$ values, with the remainder necessarily corresponding to
 the alternative $p$ values. Now, for any given threshold, although we do not know {\it which} $p$ values correspond
 to  null tests  and which to alternative tests, the areas of the two components indicate {\it how many} $p$ values correspond to each,
 allowing the FDR to be estimated (Figure \ref{fig:qvalue}).

 Of course \qvalue is not the only approach to estimating False Discovery Rates. Indeed, there is such a large
 literature on FDR methods that we do not attempt a comprehensive review. Instead we highlight the two methods that
 seem most relevant to our work here. The first is due to \cite{efron.xx}, implemented in the R package \locfdr.
 This method differs from \qvalue in that, instead of working with $p$ values, it works with $z$ scores.
 Analagous to \qvalue, \locfdr attempts to decompose the overall distribution of $z$ scores into two constitutive components,
 one corresponding to the null tests, and the other corresponding to the alternative tests. 
 In the simplest case
 \locfdr  makes assumptions analogous to the two key assumptions of \qvalue: i) the null $z$ scores have a $N(0,1)$ distribution,
 and ii) the $z$ scores near 0 are from the null, which Efron
calls the ``Zero Assumption" (ZA). Under these assumptions, \locfdr can decompose the
overall distribution of $z$ scores into a null and alternative component, and estimate the local FDR for each observation. 
 (An important focus of Efron's work \cite{}, also implemented in \locfdr, 
 is to relax the assumption that the null $z$ scores are $N(0,1)$, to allow for empirical deviations from this
theoretical null distribution. Although important, this issue is largely orthogonal to the issues we focus on here, which arise
even if the theoretical null distribution holds precisely in the empirical data, and so we consider it just briefly in the Discussion.)

Another method for FDR estimation, and perhaps the one most closely related to our
work here, is due to \cite{muralidharan.xx}, implemented in the R package \mixfdr.
Like \locfdr, \mixfdr works with $z$ scores, but it differs in that it {\it explicitly} models the alternative
distribution of $z$ scores (using a mixture of normal distributions). In principle this approach also differs from \qvalue and \locfdr in
that it does not explicitly make the Zero Assumption. However, we have found that in practice the results often approximately satisfy the ZA,
which we believe to be due to details in the fitting procedure used.

Figure \ref{fig:qvalue} illustrates these three methods in a simple simulated setting.

Efron models the overall distribution of $z$ scores using a non-parametric regression approach, and then ``subtracts out" the
null component, leaving the remainder to be the alternative component.

@@

\begin{figure}
\center \includegraphics[height=6in]{Rcode/figures/decomp_ZA.pdf}
\caption{Comparison of the way that different methods decompose $p$ values (left) and $z$ scores (right) into a null component (dark blue) and an alternative component (light blue). In the $z$ score space the alternative distribution is placed on the bottom to highlight the differences in its shape among methods.
The three existing methods (\qvalue, \locfdr, \mixfdr) all effectively make the Zero Assumption, which results in a ``hole" in the alternative $z$ score distribution around 0.
In contrast the method introduced here (\ashr) assumes that the effect sizes (and thus the $z$ scores) have a unimodal distribution about 0, resulting in a very different decomposition that in this case is much closer to the truth. (These data were simulated under a model where all of the effects are non-zero -- specifically, $\beta_j \sim N(0,1)$, $s_j=1$, resulting in $z_j \sim N(0,2)$ -- so the ``true" decomposition would make everything light blue.)} \label{fig:ZA}
\end{figure}

\subsection*{Problems with existing methods}

@@

 In outline, we use an ``Empirical Bayes" hierarchical model to combine information across measurements and perform inference.
 Here performing inference means obtaining an (approximate) posterior distribution for each effect $\beta_j$,
which can be used to estimate False Discovery Rates, and to produce both point and interval estimates for $\beta_j$.
 Although ``multiple comparisons" is usually presented as a ``problem", our emphasis here is that the multiple measurements
 actually provide an opportunity: the hierarchical model combines information across measurements to improve both accuracy and precision of estimates.

 Specifically we assume that the effects $\beta_j$ are independent and identically distributed from some unknown distribution $g(\cdot)$,
 \begin{equation} \label{eqn:beta}
 \beta_j \sim g(\cdot),
 \end{equation}
 where $g$ will be estimated from
 the data.   
  Our methods further make the following key assumptions, which distinguish them from most previous work in this area:
   \begin{enumerate}
  \item[A1:] The distribution $g(\cdot)$ is unimodal. (We assume here that the mode is at 0, although 
this could be relaxed.)  
 \item[A2:] The likelihood $L(\beta) := p(D | \beta)$ can be approximated by $\hat{L}(\beta) := \prod_j \hat{L}_j(\beta_j)$ where
 $\hat{L}_j(\beta_j) := p(\bhat_j | \beta_j, \shat_j)$ is given by (\ref{eqn:betahat-t}).
Equivalently
  \begin{equation} \label{eqn:lik}
 \hat{L}(\beta) \propto \prod_j t_\nu((\beta_j-\bhat_j)/\shat_j)
 \end{equation}
 where $t_\nu$ denotes the density of the standard $t$ distribution on $\nu$ degrees of freedom.
%which, in light of (\ref{eqn:betahat}), is equivalent to
 % \begin{equation} \label{eqn:lik2}
% L(\beta_j) \propto p(\bhat_j | \beta_j, \shat_j).
 %\end{equation}
 \end{enumerate}

@@

Although the unimodal assumption, A1, will not apply to all situations, we argue that it will be reasonable in many practical contexts. 
For example, in contexts where interest focusses on which $\beta_j$ differ from zero, which suggests that ``$\beta_j=0$" is a plausible null hypothesis,  
it seems reasonable to expect that ``$\beta_j$ very near 0" is also plausible, and that the distribution of the effects will be unimodal about 0. 
Alternatively, we can motivate A1 by its effect on point estimates, which is to ``shrink" the estimates towards the mode - 
such shrinkage is desirable from several standpoints for improving estimation accuracy. 
Note that assumption A1 relates to the distribution of {\it all} effects, and not only the {\it detectable} effects (i.e.~those that are significantly different from zero). It is very likely that the distribution of {\it detectable} non-zero effects will be multimodal, with one mode for detectable positive effects and another for detectable negative effects, and A1 does not contradict this.

Interestingly, although the unimodal assumption A1 seems natural, much previous related work on estimating False Discovery Rates  
has assumed, either explicitly or implicitly, that the distribution of effects is multimodal - see Figure \ref{fig:ZA}. 
In contrast, almost all analogous work in large-scale regression assumes the effects (regression coefficents) to have a unimodal prior distribution - 
common choices being the spike and slab, Laplace, $t$, normal-gamma, normal-inverse-gamma, or horseshoe priors.
One of our aims here is to emphasize the considerable practical benefits of making the unimodal assumption in the FDR context.

Assumption A2 can derived from an assumption of conditional independence of the data on each effect given the true effects, plus two additional assumptions: a) $\bhat_j, \shat_j$ contain most of the information about $\beta_j$ in the data $D_j$ (i.e. they are ``approximately sufficient" for $D_j$); and b) $\shat_j$ alone contains little information about $\beta_j$. The former (a) suggests the approximation $\hat{L}_j(\beta_j) \propto p(\bhat_j, \shat_j | \beta) = p(\bhat | \beta, \shat_j) p(\shat_j | \beta)$, while the latter (b) suggests assuming that $p(\shat_j|\beta_j)$ does not depend on $\beta_j$. Putting these two together yields $\hat{L}_j(\beta_j) \propto p(\bhat_j | \beta, \shat_j)$. If $\bhat_j, \shat_j$ are not sufficient for $D_j$ then there is some loss of efficiency in making this approximation, but all Bayesian inferences remain valid provided they are interpreted as conditional on $\bhat_j,\shat_j$, rather than conditional on $D_j$. See \cite{johnson:2008} and \cite{wakefield:2009} for more general discussion and examples of Bayesian inference based on summary statistics.

Alternatively A2 could be considered definitional for $\bhat_j,\shat_j$: that is, choose $\bhat_j,\shat_j,\nu$ such that A2 holds.

While Assumption A2 has parallels with approaches like \cite{efron2008microarrays, sun2007oracle}
 that model the $Z$ scores $Z_j = \bhat_j/\shat_j$ as normally distributed under the null, 
there is an important difference: here, observations with a large $\shat_j$ have an essentially flat likelihood (\ref{eqn:lik}), and so do not affect inference for
$g$ or the other effects, whereas when modeling the $Z$ scores directly, observations with large $\shat_j$ produce $Z$ scores with an $N(0,1)$ distribution that {\it do} affect inference.  Because of this our approach can take better account of the informativeness of each measurement, as illustrated in Results below.

@@

In practice, we implement the unimodal assumption (A1) by assuming a parametric finite mixture for $g$, 
\begin{equation} \label{eqn:g}
g(\cdot; \pi) = \pi_0 \delta_0(\cdot) + \sum_{k=1}^K \pi_k f_k(\cdot) 
\end{equation}
where $\delta_0(\cdot)$ denotes a point mass at 0, $\pi=(\pi_0,\dots,\pi_K)$ are mixture proportions to be estimated (with $\pi_j \geq 0, \sum_j \pi_j=1$), and $f_k$ are pre-specified 
component distributions with one of the following forms: 
\begin{enumerate}[i)]
\item $f_k(\cdot) = N(\cdot; 0, \sigma^2_k)$
\item $f_k(\cdot) = U[\cdot; -a_k,a_k]$
\item $f_k(\cdot) = U[\cdot; -a_k,0] \text{ or } U[\cdot; 0,a_k]$,
\end{enumerate}
where $N(\cdot; 0,\sigma^2)$ denotes the density of a normal distribution with mean 0 and variance $\sigma^2$ and
$U[\cdot; a,b]$ denotes the density of a uniform distribution on $[a,b]$.
That is, the non-zero effects are modeled as either i) a mixture of zero-centered normal distributions; ii) a mixture of zero-centered uniform distributions;
or iii) a mixture of ``zero-anchored" uniform distributions, which have one end of their range at 0. These approaches closely mirror approaches in \cite{cordy1997deconvolution}.

To see the flexibility of the representation (\ref{eqn:g})
think of $K$ as being ``large", with the values of $\sigma^2_k$ or $a_k$ 
spanning a wide range of values, from
essentially zero to unnecessarily large. In this way, as $K$ increases, the three different choices for $f_k$ can allow $g$ to approximate,
with arbitrary accuracy,
\begin{enumerate}[i)]
\item any scale mixture of normals, which includes as special cases
the double exponential (Laplace) distribution, any $t$ distribution, and a very large number of other distributions used in 
high-dimensional regression settings such as the spike and slab prior, the horseshoe prior \ref{}, or the more general three-parameter beta prior \ref{}.
\item any symmetric unimodal distribution about 0.
\item any (asymmetric) unimodal distribution about 0.
\end{enumerate}
The latter two claims are related to characterizations of unimodal distributions due to Khintchine (1938) and  Shepp (1962); see Feller, 1971, page  158. 
Furthermore, although it is natural for statisticians to worry about ``overfitting" if $K$ is large, 
in fact the unimodal constraint is sufficient to prevent serious problems with overfitting. For example, note that the unimodal
constraint is sufficiently strong that there will exist a non-parametric
maximum likelihood estimate (NPMLE) for $g$ under this constraint. (Indeed, if the $\beta_j$ are observed without error, corresponding to the standard errors $\shat_j \rightarrow 0$, this NPMLE has an explicit and elegant form; \cite{grenander1956theory}.)
Thus allowing $K$ to be large in ii) or iii) can be thought of as approximating the NPMLE for $g$, under the constraints of symmetry and unimodality (ii), or unimodality alone (iii).

@@

@@

>>>>

Since its introduction in 1995 by Benjamini and Hochberg 
\cite{benjamini1995controlling}, the ``False Discovery Rate" (FDR) has quickly established itself
as a key concept in modern statistics, and the primary tool by which most practitioners handle large-scale multiple testing
in which the goal is to identify the non-zero ``effects" among a large number of imprecisely-measured effects.

Here we consider an Empirical Bayes (EB) approach to FDR. This idea is, of course, far from new:
EB approaches to this problem have been quite extensively studied by several authors, 
especially B.~Efron and co-authors 
\cite{efron2001empirical, efron2002empirical,efron2003robbins,efron2008microarrays,efron2010large}; 
see also \cite{kendziorski2003parametric,newton2004detecting, 
datta2005empirical,muralidharan2010empirical} for example.
So what is the ``New Deal" here? We introduce two simple new ideas that can substantially improve
inference. The first idea is to {\it assume that the distribution of the non-zero effects is unimodal}, and to perform
non-parametric inference under this assumption. This idea has the twin benefits of both simplifying and
improving inference, at least when the assumption is correct. And even when the assumption is incorrect, we show
that the approach can be relatively robust to this. The second idea is to use two numbers (effect sizes, and their standard errors), rather than just one ($p$ values, or $z$ scores)
 to summarize each measurement. This idea allows any differences in the precision of different measurements to be taken into account,
 and in particular avoids the problem that poor-precision measurements can contaminate high-precision measurements, resulting in inflated FDR values.

In addition to these two new ideas, we highlight a third idea that is old, but which remains under-used in practice:
the idea that it may be preferable to focus on estimation rather than on testing.
In principle Bayesian approaches, including EB, can naturally unify testing and estimation into a single framework -- testing is
simply estimation but with a point mass of some weight on the null hypothesis that an effect is exactly zero.
However, despite ongoing interest in this area from both frequentist \cite{benjamini2005false} and Bayesian \cite{zhao2012empirical,gelman2012we} 
perspectives, in practice, large-scale studies that assess many effects almost invariably focus on testing significance, and
controlling the FDR, rather than on estimating the sizes of the effect. 
The two new ideas highlighted above 
help facilitate estimation as well as testing, and by providing simple software to implement our methods
we hope to promote and accelerate the shift in this direction.

@@

 \subsection*{Notation}

Suppose that we are interested in the values of $J$ ``effects" $\beta_j$ ($j=1,\dots,J$). In some contexts our interest may focus on which of the $\beta_j$ are ``significantly" different from zero, whereas in other contexts our interest may focus on estimating their values; the methods described here are suited to both these contexts.
 We assume that we have obtained data $D=(D_1,\dots,D_J)$ that provide independent estimates $\bhat_1,\dots,\bhat_J$ of these effects,
 with corresponding (estimated) standard errors $\shat_1,\dots,\shat_J$. Let $H_j$ denote the event that the $j$th null hypothesis holds, and $t_j$ denote
 the $t$ statistic testing this null:
 \begin{gather}
 H_j: \beta_j = 0 \\  
 t_j :=\bhat_j/\shat_j. 
 \end{gather}
 The $t$ statistics, of course, have a $t$ distribution under the null:
 \begin{equation} \label{eqn:tstat}
 t_j | H_j \sim T_\nu
 \end{equation}
 where $T_\nu$ denotes the $t$ distribution on $\nu$ \df, with $\nu$ assumed known. 
 Let $p_j$ denote the $p$ value obtained by comparing $t_j$ with its null distribution,
 \begin{equation}
 p_j := \Pr(|T_\nu| > |t_j| ).
 \end{equation}
Some methods for FDR analysis require $z$ scores instead of $t$ statistics or $p$ values;
 these methods can be applied by translating each $t_j$ into a corresponding
$z$ score, which we denote $z_j$.

 %For our purposes, these estimates and standard errors could be obtained from the data
%using any method, provided they (approximately) satisfy 
% \begin{equation} \label{eqn:betahat-t}
% \bhat_j \big{|} \, \beta_j, \shat_j \sim t_\nu(\beta_j,\shat_j),
% \end{equation}
%for some known degrees of freedom (\df) $\nu$, where $t_\nu(\mu,\sigma)$ denotes the generalized $t$ distribution on $\nu$ \df, with mean $\mu$ and scale parameter $\sigma$. (Equivalently, $(\bhat_j-\beta_j)/\shat_j \big{|} \, \beta_j \sim t_\nu$, where $t_\nu$ denotes the standard $t$ distribution on $\nu$ \df.)
%In the special case $\nu \rightarrow \infty$ this includes the situation where the $\bhat$ can be considered normally distributed:
%  \begin{equation} \label{eqn:betahat-norm}
% \bhat_j  \big{|} \, \beta_j, \shat_j \sim N(\beta_j,\shat^2_j).
% \end{equation}
% Assuming (\ref{eqn:betahat-t}), the $t$-statistics defined by

Let $\Gamma$ denote a subset of the tests $1,\dots,J$ declared ``significant" by some procedure. 
We define the FDR for $\Gamma$ as the proportion of these tests that are ``false discoveries" in that $H_j$ is true:
\begin{equation} \label{eqn:FDR}
\FDR(\Gamma) := \frac{\#\{j: H_j \cap j \in \Gamma\}}{\#\{j: j \in \Gamma\}},
\end{equation}
taken to be 0 if both numerator and denominator are 0. Frequentist approaches to controlling the FDR attempt to control
the expectation of $\FDR(\Gamma)$ where the expecation is taken over the sampling distribution of $\Gamma$ (which is a function of the procedure
used, considered fixed, and the data $D$, considered random). Bayesian approaches, in contrast, condition on the observed data, and compute
the posterior distribution for the $H_j$ given the data, which induces a posterior distribution on $\FDR(\Gamma)$. This posterior
distribution can be used to obtain a point estimate for $\FDR(\Gamma)$, for example using the posterior mean. 
To be more explicit, Bayesian (and EB) approaches give the posterior probability that $H_j$ holds, which
analagous to \cite{efron2008microarrays} we refer to as the ``local FDR", and denote $\fdr_j$:
%\begin{equation} \label{eqn:FDR}
%\FDR(T) := \Pr(\text{$H_j$ false} | t_j \geq T).
%\end{equation}
\begin{equation} \label{eqn:fdr}
\fdr_j := \Pr(H_j | D).
\end{equation}
The FDR can be estimated by the posterior mean for $\FDR(\Gamma)$, given by
\begin{equation} 
\widehat\FDR(\Gamma) := \frac{\sum_{j \in \Gamma} \fdr_j }{\#\{j: j \in \Gamma\}}.
\end{equation}

The $q$ value for observation $j$ is defined \cite{storey.03} as, roughly, the FDR for the set of observations that are at least as significant as observation $j$.
In a Bayesian analysis it is natural to order the significance of the hypotheses by $\fdr_j$, so we define
\begin{equation}
q_j := \FDR(\{k:\fdr_k \leq \fdr_j\}).
\end{equation}
For existing EB methods (but not for our method), typically $\fdr_j$ is a monotonic function of the $p$ value $p_j$, and so
\begin{equation}
q_j = \FDR(\{k:p_k \leq p_j\})
\end{equation}
which is close to the definition in \cite{storey.03}.

One nice feature of FDR procedures is that Frequentist and Bayesian procedures are often closely aligned, at least under certain assumptions; see
for example \cite{storey.03}, particularly his Theorem 1.

\subsection{Existing methods}

\subsubsection{qvalue}

One standard genomics analysis pipeline is to take the $p$ values $p_1,\dots,p_J$ and use them to estimate $q$ values $q_1,\dots,q_J$
 using the R package \qvalue.
  Figure \ref{fig:qvalue} shows a graphical illustration of the procedure implemented in \qvalue. 
 In brief, the idea is that the overall distribution of $p$ values can be decomposed into two constitutive
 components: one component corresponding to the ``null" tests, and a second component corresponding to the ``alternative" tests. 
To perform this decomposition, \qvalue makes two key assumptions:
  i) the null $p$ values have a uniform distribution, and ii) the $p$ values near 1 are all from
 tests where the null is true. Under these assumptions performing the decomposition boils down to 
 drawing the horizontal line on the $p$ value histogram that intersects with the distribution at $p=1$: the area under this horizontal
 line defines the uniform component that is due to the null $p$ values, with the remainder necessarily corresponding to
 the alternative $p$ values. Now, for any given threshold, although we do not know {\it which} $p$ values correspond
 to  null tests  and which to alternative tests, the areas of the two components indicate {\it how many} $p$ values correspond to each,
 allowing the FDR to be estimated (Figure \ref{fig:qvalue}).

\subsubsection{EB approaches: \locfdr and \mixfdr}

The fundamental
 idea of EB procedures is similar to that of \qvalue: to attempt to partition the observations into null and alternative components.
Here we highlight two EB methods that
 seem most relevant to our work here and which had good software implementations at the time of writing. 
 The first is due to \cite{efron2008microarrays}, implemented in the R package \locfdr.
 This method differs from \qvalue in that, instead of working with $p$ values, it works with $z$ scores.
 %Analagous to \qvalue, \locfdr attempts to decompose the overall distribution of $z$ scores into two constitutive components,
 %one corresponding to the null tests, and the other corresponding to the alternative tests. 
 In the simplest case
 \locfdr  makes assumptions analogous to the two key assumptions of \qvalue: i) the null $z$ scores have a $N(0,1)$ distribution,
 and ii) all the $z$ scores near 0 are from the null, which Efron
calls the ``Zero Assumption" (ZA).  
The \locfdr package first estimates the overall distribution of $z$ scores using a non-parametric regression approach, and then, using the two assumptions,  ``subtracts out" the
null component, leaving the remainder to be the alternative component. In this way \locfdr, like \qvalue, avoids explicit modelling of the alternative component.
 (An important focus of Efron's work, also implemented in \locfdr, 
 is to relax the assumption that the null $z$ scores are $N(0,1)$, to allow for empirical deviations from this
theoretical null distribution. Although important, this issue is largely orthogonal to the issues we focus on here, which arise
even if the theoretical null distribution holds precisely in the empirical data, and so we consider it just briefly in the Discussion.)

Another EB method, and perhaps the one most closely related to our
work here, is due to \cite{muralidharan2010empirical}, implemented in the R package \mixfdr.
Like \locfdr, \mixfdr works with $z$ scores, but it differs in that it {\it explicitly} models the alternative
distribution of $z$ scores, using a mixture of normal distributions. In principle this approach also differs from \qvalue and \locfdr in
that it does not explicitly make the Zero Assumption. However, we have found that in practice the results often approximately satisfy the ZA,
which we believe to be due to details in the fitting procedure used.

@@

@@

 Here we introduce an EB method, which, for reasons discussed below, we call ``adaptive shrinkage" or ``ash".
 The method provides not only estimated $\fdr_j$ and q values, but also shrinkage point estimates, shrinkage credible intervals,
 and estimates of the local false sign rate, defined below. It is implemented in the R package \ashr available at \url{http://github.com/stephens999/ashr}.

  Rather than directly modelling the distributions of the $p$ values, or $z$ scores, our starting point is to model the distribution of the effects $\beta_j$.
 Specifically we assume that the effects $\beta_j$ are independent and identically distributed from some unknown distribution $g(\cdot)$,
  \begin{equation} \label{eqn:beta}
 \beta_j \sim g(\cdot).
 \end{equation}
 A key assumption, which distinguishes our approach from previous work, is that $g$ is unimodal. We assume here that the mode is at 0, and allow
 that $g$ can have a point mass at 0, corresponding to the ``null" effects. 
 (An addition to our software implementation, due to C.Dai, allows the mode to be estimated from the data.)

 \def\dt{\text{dt}}

To perform likelihood-based inference for $g,\beta$, we assume that the likelihood $L(\beta) := p(D | \beta)$ can be approximated by 
$\hat{L}(\beta) := \prod_j \hat{L}_j(\beta_j)$ where
 $\hat{L}_j(\beta_j) := p(\bhat_j | \beta_j, \shat_j)$ is given by 
  \begin{equation} \label{eqn:lik}
 \hat{L}_j(\beta_j) \propto \dt_\nu(\bhat_j; \beta_j, \shat_j)
 \end{equation}
 where $\dt_\nu(\cdot; \mu,\sigma)$ denotes the density of the generalized $t$ distribution on $\nu$ degrees of freedom with mean $\mu$ and scale parameter $\sigma$ (i.e. the density of $\mu+\sigma T_\nu$). In the special case $\nu \rightarrow \infty$ this corresponds, of course, to a normal approximation to the likelihood:
  \begin{equation} \label{eqn:normlik}
 \hat{L}_j(\beta_j) \propto N(\bhat_j; \beta_j, \shat_j).
 \end{equation}
%which, in light of (\ref{eqn:betahat}), is equivalent to
 % \begin{equation} \label{eqn:lik2}
% L(\beta_j) \propto p(\bhat_j | \beta_j, \shat_j).
 %\end{equation}

@@

Although the unimodal assumption (UA) will not apply to all situations, we argue that it will be reasonable in many practical contexts. 
For example, in contexts where interest focusses on which $\beta_j$ differ from zero, which suggests that ``$\beta_j=0$" is a plausible null hypothesis,  
it seems reasonable to expect that ``$\beta_j$ very near 0" is also plausible, and that the distribution of the effects will be unimodal about 0. 
Alternatively, we can motivate  the UA by its effect on point estimates, which is to ``shrink" the estimates towards the mode - 
such shrinkage is desirable from several standpoints for improving estimation accuracy. 
Note that the UA relates to the distribution of {\it all} effects, and not only the {\it detectable} effects (i.e.~those that are significantly different from zero). It is very likely that the distribution of {\it detectable} non-zero effects will be multimodal, with one mode for detectable positive effects and another for detectable negative effects, and the UA does not contradict this.

%Interestingly, although the unimodal assumption seems natural, much previous related work on estimating False Discovery Rates  
%has assumed, either explicitly or implicitly, that the distribution of effects is multimodal - see Figure \ref{fig:ZA}. 
Note that, although the UA appears novel in this context,
almost all analogous work in large-scale regression make the UA for the regression coefficents - 
common choices of uni-modal distribution being the spike and slab, Laplace, $t$, normal-gamma, normal-inverse-gamma, or horseshoe priors \cite{}.
One of our aims here is to emphasize the considerable practical benefits of making the UA in the FDR context.

The $t$ likelihood (\ref{eqn:lik}) can derived from an assumption of conditional independence of the data on each effect given the true effects, plus two additional assumptions: a) $\bhat_j, \shat_j$ contain most of the information about $\beta_j$ in the data $D_j$ (i.e. they are ``approximately sufficient" for $D_j$); and b) $\shat_j$ alone contains little information about $\beta_j$. The former (a) suggests the approximation $\hat{L}_j(\beta_j) \propto p(\bhat_j, \shat_j | \beta) = p(\bhat | \beta, \shat_j) p(\shat_j | \beta)$, while the latter (b) suggests assuming that $p(\shat_j|\beta_j)$ does not depend on $\beta_j$. Putting these two together yields $\hat{L}_j(\beta_j) \propto p(\bhat_j | \beta, \shat_j)$. If $\bhat_j, \shat_j$ are not sufficient for $D_j$ then there is some loss of efficiency in making this approximation, but all Bayesian inferences remain valid provided they are interpreted as conditional on $\bhat_j,\shat_j$, rather than conditional on $D_j$. See \cite{johnson:2008} and \cite{wakefield:2009} for more general discussion and examples of Bayesian inference based on summary statistics.

This likelihood approximation can be motivated by assuming that i) $\bhat$
 $(\bhat_j -\beta_j)/\shat_j | \shat_j$ has a $T_\nu$ distribution, and then writing
 $p(D_j | \beta_j) = p(\bhat_j, \shat_j | \beta) = $ as sufficient for $\beta$.

Alternatively (\ref{eqn:lik}) could be considered definitional for $\bhat_j,\shat_j$: that is, choose $\bhat_j,\shat_j,\nu$ such that (\ref{eqn:lik}) holds.

A key property of the likelihood (\ref{eqn:lik}) is that
observations with a large $\shat_j$ have an essentially flat likelihood (\ref{eqn:lik}), and so do not affect inference for
$g$ or the other effects, whereas when modeling the $Z$ scores directly, observations with large $\shat_j$ produce $Z$ scores with an $N(0,1)$ distribution that {\it do} affect inference.  Because of this our approach can take better account of the informativeness of each measurement, as illustrated in Results below.
%While has parallels with approaches like \cite{efron2008microarrays, sun2007oracle}
 %that model the $Z$ scores $Z_j = \bhat_j/\shat_j$ as normally distributed under the null, 
%there is an important difference: here,

@@

In practice, we implement the UA by assuming a parametric finite mixture for $g$, 
\begin{equation} \label{eqn:g}
g(\cdot; \pi) = \pi_0 \delta_0(\cdot) + \sum_{k=1}^K \pi_k f_k(\cdot) 
\end{equation}
where $\delta_0(\cdot)$ denotes a point mass at 0, $\pi=(\pi_0,\dots,\pi_K)$ are mixture proportions to be estimated (with $\pi_j \geq 0, \sum_j \pi_j=1$), and $f_k$ are pre-specified 
component distributions with one of the following forms: 
\begin{enumerate}[i)]
\item $f_k(\cdot) = N(\cdot; 0, \sigma^2_k)$,
\item $f_k(\cdot) = U[\cdot; -a_k,a_k]$,
\item $f_k(\cdot) = U[\cdot; -a_k,0] \text{ or } U[\cdot; 0,a_k]$,
\end{enumerate}
where $N(\cdot; 0,\sigma^2)$ denotes the density of a normal distribution with mean 0 and variance $\sigma^2$ and
$U[\cdot; a,b]$ denotes the density of a uniform distribution on $[a,b]$.
That is, the non-zero effects are modeled as either i) a mixture of zero-centered normal distributions; ii) a mixture of zero-centered uniform distributions;
or iii) a mixture of ``zero-anchored" uniform distributions, which have one end of their range at 0. These approaches closely mirror approaches in \cite{cordy1997deconvolution}.
[Case i) is implemented only for the special case $\nu \rightarrow \infty$ in (\ref{eqn:like}).]

To see the flexibility of the representation (\ref{eqn:g})
think of $K$ as being ``large", with the values of $\sigma^2_k$ or $a_k$ 
spanning a wide range of values, from
essentially zero to unnecessarily large. In this way, as $K$ increases, the three different choices for $f_k$ can allow $g$ to approximate,
with arbitrary accuracy,
\begin{enumerate}[i)]
\item any scale mixture of normals, which includes as special cases
the double exponential (Laplace) distribution, any $t$ distribution, and a very large number of other distributions used in 
high-dimensional regression settings such as the spike and slab prior, the horseshoe prior \ref{}, or the more general three-parameter beta prior \ref{}.
\item any symmetric unimodal distribution about 0.
\item any unimodal distribution about 0.
\end{enumerate}
The latter two claims are related to characterizations of unimodal distributions due to Khintchine (1938) and  Shepp (1962); see Feller, 1971, page  158. 
Furthermore, although it is natural for statisticians to worry about ``overfitting" if $K$ is large, 
in fact the unimodal constraint is sufficient to prevent serious problems with overfitting. For example, note that the unimodal
constraint is sufficiently strong that there will exist a non-parametric
maximum likelihood estimate (NPMLE) for $g$ under this constraint. (Indeed, if the $\beta_j$ are observed without error, corresponding to the standard errors $\shat_j \rightarrow 0$, this NPMLE has an explicit and elegant form; \cite{grenander1956theory}.)
Thus allowing $K$ to be large in ii) or iii) can be thought of as approximating the NPMLE for $g$, under the constraints of symmetry and unimodality (ii), or unimodality alone (iii).

@@

Note use of SQUAREM.

Note penalty preferring $\pi_0$.

\subsection{various notes...}

Here performing inference means obtaining an (approximate) posterior distribution for each effect $\beta_j$,
which can be used to estimate False Discovery Rates, and to produce both point and interval estimates for $\beta_j$.
 Although ``multiple comparisons" is usually presented as a ``problem", our emphasis here is that the multiple measurements
 actually provide an opportunity: the hierarchical model combines information across measurements to improve both accuracy and precision of estimates.

@@

\subsection*{Effects of the Unimodal Assumption}

Here we consider several effects of making the UA. To isolate these effects we consider the simplest case, where every observation has the same
standard error, $s_j=1$, and we consider the normal limit (\ref{eqn:normallik}). That
is,
\begin{equation} \label{eqn:bhatgivenbz}
\bhat_j | \beta_j \sim N(0,s^2_j=1)
\end{equation}
so $z_j:=\bhat_j/s_j$ are standard normal if $H_j$ holds.
